Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
sync with policy numbers

\para{Routing policy} Routing policies in \sysname consist of an ordered sequence of both a predicate matching various classes of traffic and a list of ranked constraints on the paths that the traffic matching the predicate should prefer to take through the network. We borrow syntax from Propane~\cite{propane} but, instead of concrete prefixes and nodes, \sysname specifications can use abstract prefixes and nodes.

Let us see how to configure each of the datacenter networks from \S\ref{sec:motivation} by writing a \sysname routing policy over the abstract topology. We can capture the basic routing behavior for the datacenters with the following policy:
%
\begin{code}
\Define Routing =
    \$GP  \Path \End(TG)
    \$LP  \Path \End(TL)
    \True \Path \End(\Out) & \Exit(P1 \Prefer P2)
\end{code}
\noindent%

@@

Next we can capture the constraint that traffic for local prefixes must stay local to the datacenter.
This is written as the following \sysname constraint:
%
\begin{code}
\Define Local =
    \$LP \Path \Always(\In)
\end{code}
\noindent%
%
The Local constraint applies to any traffic destined for a local prefix described by the \$LP prefix template variable and adds the constraint that the traffic must follow a path that matches an internal location (\IE, a router inside the datacenter) at each hop of the path. This prevents traffic from ever entering from or leaving through an external peer.

It is also common practice to prevent peers (\EG, $\CD{P1}$ and $\CD{P2}$) from communicating by sending data through the datacenter. Such a constraint can be added to \sysname in the following way:
%
\begin{code}
\Define Peer = \{P1,P2\}
\Define BlockPeers =
    \True \Path !(\Enter(Peer) & \Exit(Peer))
\end{code}
\noindent%
%
We define a $\CD{Peer}$ to be either $\CD{P1}$ or $\CD{P2}$ and disallow paths where traffic both enters the datacenter through a peer and exits through a peer. Finally, we can combine these constraints together as follows:

\begin{code}
Routing & Local & BlockPeers & \Agg(PG, \In -> \Out)
\end{code}
\noindent%

This tells \sysname to find BGP router configurations that satisfy the conjunction of the Routing and Local constraints. It also declares an additional constraint that we want to perform prefix summarization (as PG) for global prefixes at the border of the datacenter (\IE, along any edge starting inside our datacenter and ending at a peer outside the datacenter).

>>>>

\para{Routing policy} Routing policies in \sysname consist of an ordered sequence of both a predicate matching a class of traffic and a list of ranked constraints on the paths that the traffic matching the predicate should prefer to take through the network. We borrow syntax from Propane~\cite{propane} but, instead of concrete prefixes and nodes, \sysname specifications can use abstract prefixes and nodes.

Let us see how to configure each of the datacenter networks from \S\ref{sec:motivation} by writing a \sysname routing policy over the abstract topology. We can capture the basic routing behavior, constraints (1, 2, 6), for the datacenters with the following policy:
%
\begin{code}
\Define Routing =
    \$GP  \Path \End(TG)
    \$LP  \Path \End(TL)
    \True \Path \End(\Out) & \Exit(P1 \Prefer P2)
\end{code}
\noindent%

@@

Next we can capture constraint (4) that traffic for local prefixes must stay local to the datacenter:
%
\begin{code}
\Define Local =
    \$LP \Path \Always(\In)
\end{code}
\noindent%
%
The Local constraint applies to any traffic destined for a local prefix described by the $\CD{\$LP}$ prefix template variable and adds the constraint that the traffic must follow a path that matches an internal location (\IE, a router inside the datacenter) at each hop of the path.
%
The constraint to prevent "valleys" (5) is implemented as:
%
\begin{code}
\Define NoValley =
    \True \Path \Novalley(\{TG,TL\},\{AG,AL\},\{S\})
\end{code}
\noindent%
%
This policy applies to all traffic and prevents valley paths by adding the $\Novalley$ constraint with arguments corresponding to each datacenter level.
%
Constraint (7) to prevent transit traffic between neighbors is expressed in \sysname as:
%
\begin{code}
\Define Peer = \{P1,P2\}
\Define NoTransit =
    \True \Path !(\Enter(Peer) & \Exit(Peer))
\end{code}
\noindent%
%
We define a $\CD{Peer}$ to be either $\CD{P1}$ or $\CD{P2}$ and disallow paths where traffic both enters the datacenter through a peer and exits through a peer. Finally, we can combine these constraints together as follows:

\begin{code}
Routing & Local & NoTransit & 
NoValley & \Agg(PG, \In -> \Out)
\end{code}
\noindent%

This instructs \sysname to find BGP router configurations that satisfy the conjunction of the Routing and Local constraints. It also declares an additional constraint that we want to perform prefix summarization (as PG) for global prefixes at the border of the datacenter (\IE, along any edge starting inside our datacenter and ending at a peer outside the datacenter).
